A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-01-26 manuscript.Rmd
divide taking and including screenshot

And Git can tell you anytime what has changed.

<!--insert screenshot-->

We recommend to attend an online lecture or workshop to learn the ins and outs of Git.

>>>>

And Git can show you what has changed, like in Figure \@ref(fig:idea-change).

```{r idea-change-screenshot, include=FALSE}
# unfortunately css selectors won't work for pdf so we'll use png instead
idea_change <- here::here("images", "idea-change.png")
webshot2::webshot("https://github.com/aaronpeikert/repro-tutorial/commit/5b3f4641ff542158184f85d458880c35e8f09f3c?diff=split",
                  file = idea_change,
                  selector = "div#diff-2f8beaa39e5c98706d8abb3361a8383776f8df8a195a21c0e6eeb25e5aa48f45", # only select file change
                  zoom = 2)# higher resolution
```

```{r idea-change, echo=FALSE, fig.cap="A screenshot of how a change tracked in Git is represented by GitHub.  ", out.width='100%'}
knitr::include_graphics(idea_change)
```
<!--I am troubled by how we should recomend to learn git-->
We recommend to attend an online lecture or workshop to learn the ins and outs of Git.
